---
title: "Initial Korean covid 19"
author: "Elisa Gonzalez"
date: "10/07/24"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?




## Graphical results - use ggplot commands to do this  


```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```


The female group had more people alive than dead while the male group had many deaths. About 55% female to the males 45% survival rate. Meaning there is a major difference between the death rate of males and the death eate of females. With males dying at a higher rate. 
  
  
## Numerical results


## Inferential results 




## Conclusions

